Analysis of Toronto Homeless Shelter System

### 2023-01-28 outputs/paper/paper.qmd
created single tables

```{r}
library(tidyverse)
library(janitor)
library(dplyr)
library(ggplot2)
library(opendatatoronto)
```

```{r}
###Read in Data####
raw_shelter_data<-
  read_csv(
    file = 
      "https://ckan0.cf.opendata.inter.prod-toronto.ca/dataset/ac77f532-f18b-427c-905c-4ae87ce69c93/resource/237d5eff-ba47-46c4-8717-a92a802abdf7/download/toronto-shelter-system-flow.csv",
    show_col_types = FALSE
  )
write_csv(
  x = raw_shelter_data,
  file = "to_shelter_system.csv"
)
head(raw_shelter_data)
tail(raw_shelter_data)
```

```{r}
####Basic Cleaning ###
raw_shelter_data<-
  read_csv(
    file = "to_shelter_system.csv",
    show_col_types = FALSE
  )
# Make the names easier to type
cleaned_shelter_data <-
  clean_names(raw_shelter_data)

@@

>>>>

```{r}
library(tidyverse)
library(janitor)
library(dplyr)
library(ggplot2)
library(kableExtra)
library(opendatatoronto)
```

```{r}
#| echo: false
###Read in Data####
raw_shelter_data<-
  read_csv(
    file = 
      "https://ckan0.cf.opendata.inter.prod-toronto.ca/dataset/ac77f532-f18b-427c-905c-4ae87ce69c93/resource/237d5eff-ba47-46c4-8717-a92a802abdf7/download/toronto-shelter-system-flow.csv",
    show_col_types = FALSE
  )
write_csv(
  x = raw_shelter_data,
  file = "to_shelter_system.csv"
)
head(raw_shelter_data)
tail(raw_shelter_data)
```

```{r}
#| echo: false
####Basic Cleaning ###
raw_shelter_data<-
  read_csv(
    file = "to_shelter_system.csv",
    show_col_types = FALSE
  )
# Make the names easier to type
cleaned_shelter_data <-
  clean_names(raw_shelter_data)

@@

```{r}
#### 2018: Average Number of Actively Homeless in Each Group ####
cleaned_shelter_data|>
  select(population_group, Year, Month, actively_homeless)|>
  filter(!population_group == "All Population")|>
  filter(Year == "18")|>
  group_by(population_group)|>
  summarise(mean = mean(actively_homeless))

```

```{r}
#### 2020: Average Number of Actively Homeless in Each Group ####
cleaned_shelter_data|>
  select(population_group, Year, Month, actively_homeless)|>
  filter(!population_group == "All Population")|>
  filter(Year == "20")|>
  group_by(population_group)|>
  summarise(mean = mean(actively_homeless))
```

```{r}
#### 2022: Average Number of Actively Homeless in Each Group ####
cleaned_shelter_data|>
  select(population_group, Year, Month, actively_homeless)|>
  filter(!population_group == "All Population")|>
  filter(Year == "22")|>
  group_by(population_group)|>
  summarise(mean = mean(actively_homeless))
```
